\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-04-13 docs/paper/paper.tex
* Some graphs, rewrote experiments section

The ANN model employed in this research is a fully-connected feed-forward Multi Layer Perceptron (MLP) consists of an input layer, an output layer, and 5 hidden layers. The ANN is designed and trained to estimate containment loss in a regression configuration. We have applied $log_{10}$ to confinement loss in order to keep its numeric stability across a wide range. Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function. Table \ref{tbl:anndetails} summarizes the details of this model. We have adopted Adam \cite{kingma2014adam} as the optimizer and the mean squared error (MSE) as the loss/cost function.

Due to the nature of the problem, over-fitting is an important issue. We have used early stopping method to reduce over-fitting. In this method, it is possible to terminate and go back to a previous state if overall validation error increases. Thus instead of being forced into a worse classifier, training is terminated earlier. In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.

In proposed system, the ANN is trained using the samples from the original dataset and the augmented samples generated by the GAN phase. Additionally, we use z-score normalization (standardization). The parameters to the normalizer is calculated through training samples and it is applied to all samples that will be used with the regressor. This includes testing and training samples. Please note that the samples that are selected to be used in training is not used in the training phase and any normalization that is applied to them are applied during testing phase.

@@

\def\dszero{Zero}

In order to prove the effectiveness of the proposed setup, we have performed multiple experiments over two datasets. We have built the first dataset that is used in the experiments. This is \hl{an SPR PCF configuration ... and collected using FV-FEM.} Details of this dataset is explained in Section \ref{sec:pcf} and it is referred as SPR dataset. Seven configurations were randomly selected for training both the GAN and the ANN, one configuration was held out for validation, and the last one is used for testing. Slicing the data this way allowed us to guide the network to predict the loss on a completely different configuration. Please note that we have applied $log_{10}$ to confinement loss to scale it.

Additionally, we have used the dataset that has been used in \cite{paper0}. \hl{This dataset contains 1000 samples. Inputs to this data is .... and outputs are ....} We have only used log of confinement loss as the output. This dataset is referred as \dszero. Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.

@@

In this set of experiments, we have analyzed the performance of the proposed ANN design. The first experiment involves in training loss over SPR dataset. In this experiment, we have trained ANN model for up to 2000 epochs and reported the training loss in Figure \ref{chart:trainingmse}. According to this experiment, training our ANN architecture more than 1000 epochs does not yield any significant improvement. Therefore, we have set the training epoch limit to 1000 in subsequent experiments.

\hl{CK: continue here.}

\begin{table*}[h]
\centering
\scalebox{1.5}{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
Length of the training data-set & Learning rate& Mini batch size & $\beta_{1}$ & $\beta_{2}$\\
\hline
336 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
\hline
336 + 1000 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
\hline
336 + 2000 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
\hline
336 + 3000 & $ 2.5\times10^{-04} $ & 20  & 0.9 & 0.999 \\
\hline
    \end{tabular}
}
\caption{Hyper-parameters chosen for the ANN model, where $\beta_{1}$ and $\beta_{2}$ are a part of Adam parameters}
\end{table*}

The MSE on the training sets ranged from 0.0030 to 0.0050. For all training datasets the MSE decreased in an acceptable manner. Next, we plot the predictions the ANN model made on the test set, after training using only the original set. As shown in the following figure.

\begin{figure}
    \begin{tikzpicture}
		\begin{axis}[
		xlabel=Epochs, 
		ylabel=Training \space MSE,
		width=0.48\textwidth,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		no marks]
		\addplot[line width=1pt,solid,color=blue] %
		table{tr_loss_ann.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Training MSE of the ANN model}
	\label{chart:trainingmse}
\end{figure}

\begin{figure}
\begin{tikzpicture}
	\begin{axis}[
		legend pos=north west,
		xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
		ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
		title={Length of the training dataset = 336 + 0},
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth
	]
		\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red
		] table{dataset_336.txt};
		\addlegendentry{$Predicted$}

		\addplot[
			line width=1pt,
			solid,color=blue
		] table{y.txt};
		\addlegendentry{$Actual$}

	\end{axis}
\end{tikzpicture}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			xlabel=$Epochs$, 
			ylabel=$ Training $ $ MSE $,
			title={Training loss function of the Critic network},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[line width=1pt,solid,color=blue]  %
			table{wgan_tr_loss.txt};
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 1000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_1000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 2000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_2000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 3000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_3000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\caption{}
\end{figure}

It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(5).
The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used. 
\begin{figure}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.33}$},
			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{133.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth, 
			line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{133.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
 \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.34}$},
			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{134.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth,
			line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{134.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
 \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			title={$n_{analyte=1.35}$},
		    xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table[x={X},y={Y_REAL}]{135.txt};
			\addlegendentry{$Actual$}
			\addplot[smooth,line width=1pt,solid,color=blue]  %
			table[x={X},y={Predictions}]{135.txt};
			\addlegendentry{$Predictions$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\caption{}
\end{figure}

@@

This work had been conduct on a  laptop:

\begin{itemize}
\item Intel(R) Core(TM) i7-5600 CPU @2.60GHz (4 CPUs)
\item 8GB RAM
\item No GPU on board
\end{itemize}

For comparaison purposes we ran the expirements on a machine with GPU on board:

\hl{CEM PC SPECS}

@@

The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.
\newline
The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, mini batch size, dataset size, number of epochs, the framework used to code the model, and of course the specifications of the machine.
In this work we fixed the number of epochs to 2000 and executed training using Tensorflow(Keras) and Pytorch frameworks. As demonstrated in Tables(5,6). It is worth mentioning the differences between training with full batch or mini batches. In full batch training, the whole dataset is passed to the model for each iteration. In contrast, mini-batch-training, the dataset is split into small mini batches of equal sizes, then passed to the model seperately, thus for each epoch there will be exactly length  of the dataset devided by the mini batch size steps, and hence slowing down the training process. Previous works \cite{masters2018revisiting, keskar2016large} have firmly proved the advantages of using the correct mini batch size as oppose to large batch sizes. Mini batches allow for more frequent gradient calculations, that results in more stable and reliable training. Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap". Active research \cite{hoffer2017train} is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime. A closely related recent work \cite{paper0}, conducted their expirements using full batch to train the model. In this work we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes. Finally, we compare the performance of the WGAN model, using Tensorflow(Keras) framework, of CPU based to that of GPU based.

@@

\hl{WGAN EXCUTION WITH GPU VS CPU BY CEM}

Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(7). This result is absolutely staggering. The ANN model calculated 48 confinement losses in just 0.17 seconds, while simulations took about 2 hours. Therefore, a well trained ANN model can be used to accurately find the best PCF geometric properties set that maximisez the distance between the confinement loss distributions of each analyte in a matter of seconds to minutes. Hence, accelerate the search for the best PCF sensor.

>>>>

The ANN model employed in this research is a fully-connected feed-forward Multi Layer Perceptron (MLP) consists of an input layer, an output layer, and 5 hidden layers. The ANN is designed and trained to estimate containment loss in a regression configuration. We have applied $log_{10}$ to confinement loss in order to keep its numeric stability across a wide range. Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function. Table \ref{tbl:anndetails} summarizes the details of this model.

We have adopted Adam \cite{kingma2014adam} as the optimizer and the mean squared error (MSE) as the loss/cost function. In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift. In proposed system, the ANN is trained using the samples from the original dataset and the augmented samples generated by the GAN phase.

@@

\def\dszero{PCF}

In order to prove the effectiveness of the proposed setup, we have performed multiple experiments over two datasets. We have built the first dataset that is used in the experiments. This is \hl{an SPR PCF configuration ... and collected using FV-FEM.} Details of this dataset is explained in Section \ref{sec:pcf} and it is referred as SPR dataset. Having nine configurations, we have performed 9-fold testing on this dataset. Each fold tests a single configuration using the other configurations as training data. Slicing the data this way allowed us to guide the network to predict the loss on a completely different configuration. Please note that we have applied $log_{10}$ to confinement loss to scale it.

Additionally, we have used the dataset that has been used in \cite{paper0}. \hl{This dataset contains over 1000 samples. Inputs to this data is .... and outputs are ....} We have only used log of confinement loss as the output. This dataset is referred as \dszero. Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.

@@

In this set of experiments, we have analyzed the performance of the proposed ANN design. The first experiment involves in training loss over SPR dataset. In this experiment, we have trained ANN model for up to 2000 epochs and reported the training loss in Figure \ref{chart:trainingmse}. According to this experiment, training our ANN architecture more than 1000 epochs does not yield to any significant improvement. Therefore, we have set the training epoch limit to 1000 in subsequent experiments. Additionally, it is clear that the use of augmented samples from the GAN phase reduces the oscillations in the training error.

We have performed experiements comparing the proposed ANN architecture with the state-of-the-art method proposed in \cite{paper0}. Results of this experiment is demonstrated in Figure \ref{chart:perfnoaug}. Please note that in the experiment involving SPR dataset, ANN models are predicting a new configuration and the number of samples available for training is lower. Therefore, they both have higher error rate compared to the \dszero{} dataset.

\begin{table*}[h]
\hl{Needs fixing}
\caption{Hyper-parameters chosen for the ANN model, where $\beta_{1}$ and $\beta_{2}$ are a part of Adam parameters}
\centering
\scalebox{1.5}{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
Length of the training data-set & Learning rate& Mini batch size & $\beta_{1}$ & $\beta_{2}$\\
\hline
336 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
\hline
336 + 1000 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
\hline
336 + 2000 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
\hline
336 + 3000 & $ 2.5\times10^{-04} $ & 20  & 0.9 & 0.999 \\
\hline
    \end{tabular}
}
\end{table*}

\begin{figure*}
	\begin{subfigure}{.48\textwidth}
	\centering
    \begin{tikzpicture}
		\begin{axis}[
		xlabel=Epochs, 
		ylabel=Training \space MSE,
		width=\textwidth,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		ymax=2,
		no marks]
		\addplot[line width=1pt,solid,color=blue] %
		table{../../experiments_spr-pcf/va_loss_curves/With augmentation/ann/ann_tr_loss.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{With augmentation}
	\end{subfigure}	
	\begin{subfigure}{.48\textwidth}
	\centering
	\begin{tikzpicture}
		\begin{axis}[
		xlabel=Epochs, 
		ylabel=Training \space MSE,
		width=\textwidth,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		ymax=2,
		no marks]
		\addplot[line width=1pt,solid,color=blue] %
		table{../../experiments_spr-pcf/va_loss_curves/Without augmentation/ann_loss_without_augmt.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Without augmentation}
	\end{subfigure}

	\caption{Training MSE of the ANN model with (a) and without (b) GAN phase obtained from SPR dataset}
	\label{chart:trainingmse}
\end{figure*}

\begin{figure*}
\begin{subfigure}{0.48\textwidth}
	\begin{tikzpicture}
		\begin{axis}[
			legend pos=north west,
			xlabel=Actual loss in $log(db/cm)$, 
			ylabel=Predicted loss in $log(db/cm)$,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=\textwidth
		]
			\addplot[
				only marks,
				mark size=2.9pt, mark=o, color=red, fill=red
			] table{../../experiments_spr-pcf/Without_augmentation/kfold-predictions-vs-labels/1st/graph_data.txt};
			\addlegendentry{$Proposed$}

			\addplot[
				only marks,
				mark size=2.9pt, mark=x, color=green
			] %table{??};
			coordinates{(7.2, 6.8)};
			\addlegendentry{\cite{paper0}}

			\draw[
				line width=1pt,
				solid,color=blue
			]
			(axis cs:\pgfkeysvalueof{/pgfplots/xmin},\pgfkeysvalueof{/pgfplots/xmin}) -- 
			(axis cs:\pgfkeysvalueof{/pgfplots/xmax},\pgfkeysvalueof{/pgfplots/xmax});
			\addlegendimage{line legend, 
				line width=1pt,
				solid,color=blue}
			\addlegendentry{$Actual$}

		\end{axis}
	\end{tikzpicture}
	\caption{SPR dataset}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
    \begin{tikzpicture}
	\begin{axis}[
		legend pos=north west,
		xlabel=Actual loss in $log(db/cm)$, 
		ylabel=Predicted loss in $log(db/cm)$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=\textwidth
	]
		\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table{../../experiments_pcf2/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
		\addlegendentry{$Proposed$}

		\addplot[
			only marks,
			mark size=2.9pt, mark=x, color=green
		] 
		%table{??};
		coordinates{(-5, -10)};
		\addlegendentry{\cite{paper0}}

		\draw[
			line width=1pt,
			solid,color=blue
		]
		(axis cs:\pgfkeysvalueof{/pgfplots/xmin},\pgfkeysvalueof{/pgfplots/xmin}) -- 
		(axis cs:\pgfkeysvalueof{/pgfplots/xmax},\pgfkeysvalueof{/pgfplots/xmax});
		\addlegendimage{line legend, 
			line width=1pt,
			solid,color=blue}
		\addlegendentry{$Actual$}

		\end{axis}
    \end{tikzpicture}
    \caption{\dszero{} dataset}
\end{subfigure}
\vspace{0.75cm}

\begin{subfigure}{\textwidth}
	\begin{tikzpicture}
	\begin{axis}[
		legend pos=north west,
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.34}$},
		width=0.48\textwidth
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	]
	table[x={wave},y={predicted}]{data/vswavelength134_fold1.txt};
	\addlegendentry{$Proposed$}

	\addplot[
		only marks,
		mark size=2.9pt, mark=x, color=green
	] 
	%table{??};
	coordinates{(500, 7)};
	\addlegendentry{\cite{paper0}}

	\addplot[
		color=blue
	] 
	table[x={wave},y={real}]{data/vswavelength134_fold1.txt};
	coordinates{(6.8, 7.2)};
	\addlegendentry{Actual}

	\end{axis}
	\end{tikzpicture}
	\begin{tikzpicture}
	\begin{axis}[
		legend pos=north west,
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.35}$},
		width=0.48\textwidth
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	] 
	table[x={wave},y={predicted}]{data/vswavelength135_fold1.txt};
	\addlegendentry{$Proposed$}

     \addplot[
		only marks,
		mark size=2.9pt, mark=x, color=green
     ]
     %table{??};
     coordinates{(500, 7.5)};
     \addlegendentry{\cite{paper0}}

	\addplot[
		color=blue
	] 
	table[x={wave},y={real}]{data/vswavelength135_fold1.txt};
	\addlegendentry{Actual}

	\end{axis}
	\end{tikzpicture}
	\caption{Configuration estimation on SPR dataset}
\end{subfigure}
\caption{Testing results without GAN augmentation phase}
\label{chart:perfnoaug}
\end{figure*}

\hl{CK: continue here..}

@@

It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(5).
The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used.

@@

@@

The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.

The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, mini batch size, dataset size, number of epochs, the framework used to code the model, and of course the specifications of the machine.

In this work we fixed the number of epochs to 2000 and executed training using Tensorflow(Keras) and Pytorch frameworks. As demonstrated in Tables(5,6). It is worth mentioning the differences between training with full batch or mini batches. In full batch training, the whole dataset is passed to the model for each iteration. In contrast, mini-batch-training, the dataset is split into small mini batches of equal sizes, then passed to the model seperately, thus for each epoch there will be exactly length  of the dataset devided by the mini batch size steps, and hence slowing down the training process. Previous works \cite{masters2018revisiting, keskar2016large} have firmly proved the advantages of using the correct mini batch size as oppose to large batch sizes. Mini batches allow for more frequent gradient calculations, that results in more stable and reliable training. Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap". Active research \cite{hoffer2017train} is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime. A closely related recent work \cite{paper0}, conducted their expirements using full batch to train the model. In this work we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes. Finally, we compare the performance of the WGAN model, using Tensorflow(Keras) framework, of CPU based to that of GPU based.

@@
